---
title: "Data and Reproducibility of the Article Robust Model-Based Clustering"
author: "Juan D. Gonzalez"
date: "2/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

This repository is for reproducing the analysis on real data of the article
_Robust Model-Based_ Clustering whose authors are Juan D. Gonzalez, [Ricardo Maronna](https://scholar.google.com/citations?user=Cqa77SYAAAAJ&hl=en), 
[Victor J. Yohai](https://scholar.google.com/citations?user=fBUfRqcAAAAJ&hl=en), and [Ruben H. Zamar](https://scholar.google.ca/citations?user=XgRp4HUAAAAJ&hl=en). 

The only thing you should do in order to reproduce the results is to download 
the repository and run in R

```{r eval= FALSE}
source("Fig2_and_Table3.R")
```
This command will do the following steps

* Install the package "RMBC" from github. This packages implements the estimator 
developed in [1] and contains the real data set used to asses our procedure. 
* Install the necessary packages from CRAN, namely
  * [`tclust`](https://cran.r-project.org/web/packages/tclust/index.html)
  * [`RSKC`](https://cran.r-project.org/web/packages/RSKC/index.html)
  * [`GSE`](https://cran.r-project.org/web/packages/GSE/index.html)
  * [`otrimle`](https://cran.r-project.org/web/packages/otrimle/index.html)
  * [`mclust`](https://cran.r-project.org/web/packages/mclust/index.html)
  * [`mvtnorm`](https://cran.r-project.org/web/packages/mvtnorm/index.html)
  * [`ktaucenters`](https://cran.r-project.org/web/packages/ktaucenters/index.html)
  * [`combinat`](https://cran.r-project.org/web/packages/combinat/index.html)
* Run the  auxiliary routines that aid to plot the results, compute performance measures and 
  give to the different estimators the same format. 
  * `auxComputeClusters.R`
  * `auxPlotGroupsModelBasedCluster.R`
  * `performance_measures.R`
  
**Reference**:   
[1] Gonzalez, J. D., Maronna, R., Yohai, V. J., & Zamar, R. H. (2021). Robust Model-Based Clustering. arXiv preprint arXiv:2102.06851.
